\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Fix space issues with "project" macro
Use siunitx macros consistently

\newcommand{\project}[1]{\textsc{#1}}
\newcommand{\Spoon}{\project{Spoon}}
\newcommand{\Guava}{\project{Guava}}
\newcommand{\Fastjson}{\project{Fastjson}}
\newcommand{\Seata}{\project{Seata}}
\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

@@

The configuration is largely identical to the established configuration used in
prior years, and mainly uses the tuned default
values~\cite{arcuri2013parameter} and default coverage criteria
\cite{rojas2015combining}.
%
As in previous years, the configuration omits the test minimisation step as the
competition score does not reward test minimality, and the minimisation takes
substantial computational effort. Similarly, the configuration includes all
regression assertions rather than filtering them with mutation analysis to save
time.
%
The time budget was again distributed by allocating 50\% of the overall time
set by the competition organisers for the search, and the other 50\% equally to
the remaining phases (e.g., assertion generation, compile-check,
flakiness-check).

>>>>

\newcommand{\project}[1]{\textsc{#1}\xspace}
\newcommand{\Spoon}{\project{Spoon}}
\newcommand{\Guava}{\project{Guava}}
\newcommand{\Fastjson}{\project{Fastjson}}
\newcommand{\Seata}{\project{Seata}}
\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

@@

The configuration is largely identical to the established configuration used in
prior years, and mainly uses the tuned default
values~\cite{arcuri2013parameter} and default coverage criteria
\cite{rojas2015combining}.
%
As in previous years, the configuration omits the test minimisation step as the
competition score does not reward test minimality, and the minimisation takes
substantial computational effort. Similarly, the configuration includes all
regression assertions rather than filtering them with mutation analysis to save
time.
%
The time budget was again distributed by allocating \SI{50}{\percent} of the overall time
set by the competition organisers for the search, and the other \SI{50}{\percent} equally to
the remaining phases (e.g., assertion generation, compile-check,
flakiness-check).
